Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Fixed not mentioning group in explanation of rendering volume behind intersection in first approach
Only one part of volume in front of intersection in first approach

Next the part of the volume behind the intersection is rendered into the results
texture.  To get just that part the back faces of the Boolean AND are used
instead of the front faces of the cube.  Note in the code snippet below we omit
the instructions for rendering the second volume and for setting uniform
variables.  We also give the intersection an ID so it can be redrawn later.

@@

After that the parts of the volumes in front of the intersection are rendered to
the results texture.  We have the shader program set the depth of the fragments
generated to the lowest value to effectively mask off that part of the screen.

>>>>

Next the part of the volume behind the intersection is rendered into the results
texture.  To get just that part the back faces of the Boolean AND are used
instead of the front faces of the cube.  Note in the code snippet below we omit
the instructions for rendering the second volume and for setting uniform
variables.  We also put the Boolean AND into a group so it can be redrawn later
without duplicating the calculations or geometry.

@@

After that the part of the volume in front of the intersection is rendered to
the results texture.  We have the shader program set the depth of the fragments
generated to the lowest value to effectively mask off that part of the screen.
